Last glacial cycle glacier erosion potential in the Alps

### 2021-05-24 articles/erosion/response-referee1.md

> Line 127 Higher precipitation increases ice flux and thus erosion, I guess?
> Would eventually helpful to mention (even though it might be referred in
> Seguinot et al., 2018).

Indeed. The increase in ice discharge was made explicit.

> Line 140 Can you be more precise what you mean by realistic? You mean because
> of the localized pattern? Maybe I am wrong but shouldn’t the erosion
> potential at least at the lake Constance overdeepening (Fig. 7) not in the
> order of hundreds of meters (cf. Preusser et al., 2010) and the best fit
> rather (b) or (c) – at least from what I read from the transect (e-h)?
> Visually (a)-(d) seem not to correspond to (e)-(h) if (a)-(d) is also
> presented in meters (annotation at the bar is missing). For example, in (b)
> the maximum erosion potential is like >>1000 m (if in meters) while in
> corresponding (f) it seems clearly lower than 1000 m.

We are not sure what the cumulative erosion potential of the last glacial cycle
should be. This sentence was about the amplitude of the cumulative erosion
potential, but we were probably a bit too fast deeming one erosion law "more
realistic" than the others. Based on the estimates of total Pleistocene glacial
relief from the suggested references, we now argue that no tested erosion law
give results in the expectable range of last glacial cycle erosion.

    With a total Pleistocene glacial relief on the order of a kilometre
    (Preusser et al., 2011; Valla et al., 2011), a cumulative glacial erosion
    for the last glacial cycle in the order of 10-100 m can be expected.
    However, none of the tested erosion power-laws fall within this range.
    Instead, the erosion law calibrated on tidewater glaciers (Koppes et al.,
    2015) yields cumulative erosion in the Rhine Valley in the orders of
    metres, while the three erosion laws based on terrestrial glaciers
    (Humphrey and Raymond, 1994; Herman et al., 2015; Cook et al., 2020},
    result in kilometre-scale integrated erosion potential. During the Last
    Glacial Maximum and much of the last glacial cycle, Alpine paleoglaciers
    were closer in size, slope (an important parameter as we argue in the next
    section), and climatic context to the present-day glaciers of Patagonia and
    the Antarctic Peninsula (Koppes et al., 2015) than to Franz-Joseph Glacier
    (Herman et al., 2015) and many of the glaciers included in the global
    compilation by Cook et al., (2020). This may help to explain why the
    reality appears to fall in-between the tested erosion laws.

Regarding Fig. 7, there is no mismatch between panels (a-d) and (e-h), but to
improve readability we have reduced the number of colour levels on the maps,
and changed the positions of ticks on the transects.

### 2021-05-24 articles/erosion/alps-erosion.tex
Improve discussion of realistic erosion magnitude.

    It may seem surprising that the erosion law calibrated on Patagonian and
    Antarctic Peninsula tidewater glaciers \citep{Koppes.etal.2015} yields a
    more realistic glacial cycle erosion potential in the Alps than those based
    on terrestrial
    glaciers \citep{Humphrey.Raymond.1994, Herman.etal.2015, Cook.etal.2020},
    themselves resulting in kilometre-scale integrated erosion even
    higher than the Alpine relief itself. However, during the Last Glacial
    Maximum and much of the last glacial cycle, Alpine paleoglaciers were
    closer in size, slope, and climatic context to the present-day glaciers of
    Patagonia and the Antarctic Peninsula \citep{Koppes.etal.2015} than to
    Franz-Joseph Glacier \citep{Herman.etal.2015} and many of the glaciers
    included in the global compilation by \citet{Cook.etal.2020}.
    \todo{rework this paragraph. The realistic laws lies in-between.}

>>>>

    With a total Pleistocene glacial relief on the order of a kilometre
    \citep{Preusser.etal.2011, Valla.etal.2011}, a cumulative glacial erosion
    for the last glacial cycle in the order of 10--100\,m can be expected.
    However, none of the tested erosion power-laws fall within this range.
    Instead, the erosion law calibrated on tidewater glaciers
    \citep{Koppes.etal.2015} yields cumulative erosion in the Rhine Valley in
    the orders of metres, while the three erosion laws based on terrestrial
    glaciers \citep{Humphrey.Raymond.1994, Herman.etal.2015, Cook.etal.2020},
    result in kilometre-scale integrated erosion potential. During the Last
    Glacial Maximum and much of the last glacial cycle, Alpine paleoglaciers
    were closer in size, slope (an important parameter as we argue in the next
    section), and climatic context to the present-day glaciers of
    Patagonia and the Antarctic Peninsula \citep{Koppes.etal.2015} than to
    Franz-Joseph Glacier \citep{Herman.etal.2015} and many of the glaciers
    included in the global compilation by \citet{Cook.etal.2020}.
    This may help to explain why the reality appears to fall in-between the
    tested erosion laws.
